### 2021-03-14 paper.Rmd
start mapping out what's left
conflict resolved and control image made larger

@@

\begin{figure*}
   \centering
         \includegraphics[width=0.5\textwidth]{figures/liminal-stop-pause-refresh.png}
\caption{The clustering example in figure \ref{fig:tsne-tour} using the liminal interface. Here a grand tour is displayed on the right hand side, with buttons allowing users to play, pause and refresh the tour animation.}
\label{fig:tour-controls}
\end{figure*}

>>>>

The rest of the paper is structured as follows...

@@

\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/liminal-stop-pause-refresh.png}
\caption{The clustering example from Figure \ref{fig:tsne-tour} using the liminal interface. Here a grand tour is displayed on the right hand side, with buttons allowing users to play, pause and refresh the tour animation.}
\label{fig:tour-controls}
\end{figure*}
